(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-03 ms.tex
Intro done!

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\project}[1]{\textsl{#1}} 
\newcommand{\kep}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand\teff{\ensuremath{T_\text{eff}}}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ Campaign 1
Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
Earth-like Insolation?)}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ Campaign 1. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary 
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The demise of two reaction wheels on the spacecraft led to a repurposing 
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are 
controlled by the two remaining reaction wheels, while the roll of the 
spacecraft is balanced with solar radiation pressure and quasiperiodic 
thruster firing.
The result of this observing strategy is that the targets appear to drift
at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain at 
approximately the same location on the detector.
Both the slow drift and the corrections are observable by eye, and by viewing the
motions of each star \citep{Barentsen15} it is apparent that \KT\ is working as 
advertised.
Therefore, apertures can be defined around each star and aperture photometry can be
defined in the usual way.

@@

\paperit{} apply an altern

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey 
\citep[SDSS DR9,][]{Ahn12}. 
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ Campaign 1 is 
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table 
\ref{Table:BGstars}.

>>>>

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\project}[1]{\textsl{#1}} 
\newcommand{\kep}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\Ci}{Campaign~1}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand\teff{\ensuremath{T_\text{eff}}}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\mjup}{{M$_\textrm{Jup}$}}
\newcommand{\rjup}{{R$_\textrm{Jup}$}}

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
Earth-like Insolation?)}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary 
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The fidelity of this sample is high, so most of these planet candidates are truly planets
\citep{Morton11b, Fressin13}.
The demise of two reaction wheels on the spacecraft led to a repurposing 
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are 
controlled by the two remaining reaction wheels, while the roll of the 
spacecraft is balanced with solar radiation pressure and quasiperiodic 
thruster firing.
The result of this observing strategy is that the targets appear to drift
at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain at 
approximately the same location on the detector.
Both the slow drift and the corrections are observable by eye, and by viewing the
motions of each star \citep{Barentsen15} it is apparent that \KT\ is working as 
advertised.
Therefore, apertures can be defined around each star and aperture photometry can be
defined in the usual way.

@@

\paperit{} simultaneously fit both the systematics and potential planetary transit signals
in a search for transiting planets. 
The authors of that paper assume that the dominant trends in the observed stellar light
curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
right? Not between?}
They then run PCA on all stars to measure the dominant modes, modeling each star as a 
linear combination of 150 of these ``eigen light curves'' and a transit signal.
This method enables fitting without over-fitting, and also permits marginalization over
uncertainties induced by the noise model.
Therefore, any uncertainties in the systematics can be propogated into uncertainties in
detected planet parameters, instead of assuming the systematics are understood perfectly.
Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
\Ci\ data.

In \paperit, only transit properties are provided, not absolute parameters about the
planet or the star. 
Additionally, the authors follow the convention of the \kep\ team to include any
transit event as a candidate system rather than a false positive if a secondary eclipse
is not detected: there is no enforced upper limit on the allowed planet radius.
The authors intentionally make no effort to separate astrophysical false positives from
true transiting planets.

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm 
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

This paper is organized as follows. 
In \textsection2, we develop stellar properties through
photometric and spectroscopic data.
In \textsection3, we combine the derived stellar properties with \KT\ data to infer planet
candidate properties.
In \textsection4, we combine adaptive optics and radial velocity observations with both
archival and modern ground-based, seeing limited survey data and an analysis of the
transit parameters to calculate false positive probabilities.
In \textsection5, we discuss potentially interesting systems.
In \textsection6, we summarize and discuss our results.

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey 
\citep[SDSS DR9,][]{Ahn12}. 
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is 
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table 
\ref{Table:BGstars}.
